---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dirigible

<!-- badges: start -->
<!-- badges: end -->

A fresh attempt at vapour. GDAL for R using a headers appraoch. 

## Installation

TBD but don't do it this will break your system 

## Example

Linux only for now.  This merely proves that I am not completely lost. 


```{r example, eval=TRUE, include=TRUE}
library(dirigible)
f <- system.file("extdata/tab/list_locality_postcode_meander_valley.tab", package = "vapour")
dirigible:::driver_gdal(f)
dirigible:::feature_count_gdal(f, layer = 0, iterate = FALSE)

dirigible:::layer_names_gdal(f)

## white zone
dirigible:::dirigible_unload_gdal()
try(dirigible:::layer_names_gdal(f))
dirigible:::dirigible_load_gdal()
dirigible:::layer_names_gdal(f)

```

---

## Code of Conduct
  
Please note that the dirigible project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
